Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-06-09 Writing/CEA_3rd_round/replies_rev.rmd
modification for the final submission

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
bibliography: ../ML_VRA.bib
---

>>>>

---
title: "Response to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
bibliography: ../ML_VRA.bib
---

### 2022-06-09 Writing/manuscript_cea.rmd
modification for the final submission

Elementary calculus shows that the necessary condition for maximization is, that $\partial f(I, \mathbf{c})/\partial I - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations. (See Figure E.1 in Appendix E for examples of visualizations of predicted and true yields along with RMSE values, by model.) Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact, along with the poor performance of RF in predicting EONR presented in \@ref(tab:table-optN), shows that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario"}
vis_RMSE_y_eonr
```

@@

We also showed that the best model in prediction yields is not necessarily the best model in predicting EONRs and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question the usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.

>>>>

Elementary calculus shows that the necessary condition for maximization is, that $p (\partial f(I, \mathbf{c})/\partial I) - w =0$, which implicitly defines the economically optimal input application rate as a function of prices and soil/field characteristics, and may be arranged as \@ref(eq:eqn2):

@@

Table \@ref(tab:table-y) shows the mean RMSE of yield prediction over the one thousand simulations. (See Figure E.1 in Appendix E for examples of visualizations of predicted and true yields along with RMSE values, by model.) Since CF-base does not predict yield, the table only reports the results from RF, BRF and CNN. Compared to the result of EONR estimation, RF performed as well as BRF in the simple modeling scenarios of "aby" and "abytt." This fact, along with the poor performance of RF in predicting EONR presented in Table \@ref(tab:table-optN), shows that strong predictive power of yield levels does not imply accurate prediction of EONR. Further, RF shows vulnerability to the inclusion of many correlated variables, as is displayed for EONR prediction as well. While CNN performed worse than RF and BRF in "aby" and "abytt," it performed better than RF in more complicated modeling scenarios, showing robustness, at least in yield prediction, to inclusion of many correlated variables. Of course, while on average in the "aabbyy" and "aabbyytt" scenarios CNN predicted yields better than RF did, CNN's EONR predictions were worse than RF's, which further backs our claim that a good yield prediction capability does not imply good EONR prediction capability.

@@

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The relationship between yield and EONR prediction performances under the aabbyytt scenario"}
vis_RMSE_y_eonr
```

@@

We also showed that the best model in predicting yields is not necessarily the best model in predicting EONRs and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question the usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.
